---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ovbfunc

<!-- badges: start -->
<!-- badges: end -->

The `ovbfunc` package implements the method for assessing the sensitivity of functions of OLS coefficients to omitted variable bias. Given a medium regression and a known function, the method computes the range of estimates consistent with assumptions in a neighborhood of that baseline. 

## Installation

You can install the development version of `ovbfunc` from its GitHub repository via

``` r
# install.packages("devtools")
devtools::install_github("peizansheng/ovbfunc")
```

## Load the Package

``` {r}
library(ovbfunc)
```

## Main Functions

`ovbfunc` provide three main functions:

``` r
sens_linear(Y, X, W1, bar_rho, bar_R2, ellipsoid = NULL, c, c0, method = "analytical")
```

where:

- `Y`: outcome (A $N \times 1$ vector)
- `X`: treatments (A $N \times d_X$ dataframe/matrix/vector)
- `W1`: observed controls (A $N \times d1$ dataframe/matrix/vector or `NULL`)
- `bar_rho`: sensitivity parameter (A scalar in $[0, 1)$)
- `bar_R2`: sensitivity parameter (A scalar in $[0, 1)$)
- `ellipsoid`: optional constraints of ellipsoid (A list computed from `precompute_ellipsoid()`)
- `c`: linear function coefficient (A $d_X \times 1$ vector)
- `c0`: linear function intercept (A scalar)
- `method`: solve method (`"analytical"` or `"gurobi"`)

``` r
sens_linear_frac(Y, X, W1, bar_rho, bar_R2, ellipsoid = NULL, c, c0, d, d0)
```

``` r
sens_general(
  Y, X, W1, bar_rho, bar_R2, ellipsoid = NULL,
  f, grad_f, beta_init, step_size = 0.01,
  max_iter = 5000, tol = 1e-8, verbose = 100
)
```

## Example

To replicate sensitivity analysis in Acemoglu et al (2008), run the following code.

```{r}
ajry_ovb_func(acemoglu_et_al_2008 = acemoglu_et_al_2008)
```
